Importance of depth refugia for reef resilience and intervention on the Great Barrier Reef under future climate change

### 2025-10-08 paper/paper_draft.qmd
Fix malformed sentence in acknowledgements

The authors acknowledge the Traditional Owners of the Sea Country on which the modelling was
conducted for. The authors additionally acknowledge the Bindal, Jagera, and Ngunnawal
Peoples on which the authors conducted the model development, analysis and writing. The
authors acknowledge the contributions of Barbara Robson and Jessica Benthuysen for comments
provided early in the manuscript preparation. The authors would like to additionally
acknowledge and thank Shaun Wilson and Juan Carlos Ortiz for discussions around carbonate
budget thresholds.

>>>>

The authors acknowledge the Traditional Owners of the Sea Country on which the modelling was
conducted for. The authors additionally acknowledge the Bindal, Jagera, and Ngunnawal
Peoples, the lands on which the authors conducted the model development, analysis, and
writing. The authors also acknowledge the contributions of Barbara Robson and Jessica
Benthuysen for comments provided early in the manuscript preparation. The authors would like
to additionally acknowledge and thank Shaun Wilson and Juan Carlos Ortiz for discussions
around carbonate budget thresholds.
